\def \CODDI {INT1}
\def \USRSI {\aag{} check the PH, humidity and temperature of the ground through the
             Arduino sensor \sic{} verify the actual plant conditions.}
\def \PoII {8}

\def \CODDII {INT2}
\def \USRSII {\aag{} see get weather for tomorrow from the metheorological center
             \sic{} see what actions will be taken.}
\def \PoIII {5}

\def \CODDIII {INT3}
\def \USRSIII {\aag{} input specific charateristics of the plant
             \sic{} track these across time}
\def \PoIIII {3}

\def \CODDIV {INT5}
\def \USRSIV {\aag{} check the historical characteristics of the plant
             \sic{} track its growth.}
\def \PoIIV {2}

\def \CODDV {INT4}
\def \USRSV {\aag{} check when was the last time actuators were activated
             \sic{} call for maintenance if necessary.}
\def \PoIV {1}

\def \CODDVI {INT6}
\def \USRSVI {\aag{} get an estimate of when to harvest
             \sic{} plan my meals.}
\def \PoIVI {13}

\def \CODDVII {INT7}
\def \USRSVII {\aag{} view every action ever taken
             \sic{} check for malfunctions.}
\def \PoIVII {2}

\def \CODDVIII {INT8}
\def \USRSVIII {\aag{} receive a message on my phone when the cultivation plan changes
             \sic{} be aware of any anomalies.}
\def \PoIVIII {8}

\def \CODDIX {INT9}
\def \USRSIX {\aag{} check the growth plan and actual status
             \sic{} modify it if its wrong.}
\def \PoIIX {5}

\def \CODDX {INT11}
\def \USRSX {\aag{} check the plan for the next 24 hours.
             \sic{} schedule more actions.}
\def \PoIX {2}

\def \CODDXI {INT10}
\def \USRSXI {\aag{} automatize the actions to take
             \sic{} follow the master plan.}
\def \PoIXI {8}

\def \CODDXII {INT12}
\def \USRSXII {\aag{} automatize the actuators activation
             \sic{} so actions can be taken automatically.}
\def \PoIXII {5}

\def \CODDXIII {GAL1}
\def \USRSXIII {\aab specify care rules
             \sic{} get warnings when the growth conditions are not ideal.}
\def \PoIXIII {3}

\def \CODDXIV {GAL2}
\def \USRSXIV {\aab input a master growth plan
             \sic{} specify growth conditions for the plant.}
\def \PoIXIV {3}

\def \CODDXV {GAL3}
\def \USRSXV {\aag{} visualize the historical values of indicators and supplies.
             \sic{} decide if the values are correct.}
\def \PoIXV {3}

\def \CODDXVI {WEB1}
\def \USRSXVI {\aag{} check via web the status
             \sic{} monitor my plant from around the world.}
\def \PoIXVI {8}



\def \anchoprod {p{14cm}}

\section{\prodback{}}


A continuaci\'on se encuentran las \textit{stories} que logramos
condensar al iniciar el trabajo pr\'actico, a partir del enunciado.

  \vspace{1cm}

\begin{small}
\begin{tabular}{ |l|\anchoprod|l| }
\hline
\multicolumn{3}{ |c| }{Product Backlog} \\
\hline
Code & User Story & Points \\
\hline
\CODDI & \USRSI & \PoII \\
\hline
\CODDII & \USRSII & \PoIII \\
\hline
\CODDIII & \USRSIII & \PoIIII \\
\hline
\CODDIV & \USRSIV & \PoIIV \\
\hline
\CODDV & \USRSV & \PoIV \\
\hline
\CODDVI & \USRSVI & \PoIVI \\
\hline
\CODDVII & \USRSVII & \PoIVII \\
\hline
\CODDVIII & \USRSVIII & \PoIVIII \\
\hline
\CODDIX & \USRSIX & \PoIIX \\
\hline
\CODDX & \USRSX & \PoIX \\
\hline
\CODDXI & \USRSXI & \PoIXI \\
\hline
\CODDXII & \USRSXII & \PoIXII \\
\hline
\CODDXIII & \USRSXIII & \PoIXIII \\
\hline
\CODDXIV & \USRSXIV & \PoIXIV \\
\hline
\CODDXV & \USRSXV & \PoIXV \\
\hline
\CODDXVI & \USRSXVI & \PoIXVI \\
\hline
\end{tabular}

\end{small}
